Generalized Tractability

### 2023-06-05 GeneralizedTractability_230529.tex
Updates from Overleaf

\begin{proof}
\textbf{Sufficient condition:}\newline
Following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n$ and $N$ with $1 \le N \le n \le M(d)$

>>>>

\begin{proof}
\textbf{Sufficient condition:}\newline
Fix $d$.  For the case where $M(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n$ and $N$ with $1 \le N \le n \le M(d)$, we have
\begin{align*}
    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d',\vp)} \\
     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
\end{align*}
Thus, we can conclude from the previous line that
\begin{multline} \label{eq:implicate_a_rest}
    n - N +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals, \ N \le n \le M(d).
\end{multline}
